Appendix

### 2022-01-10 paper/manuscript/appendix.Rmd
add code for f scores by conf threshold, lme4 tests on gold set

---
title: "Appendix"
author: "Bria Long"
date: "1/6/2022"
output: word_document
---

```{r, echo=F, message=F}
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(egg)
library(stargazer)
library(magick)
library(ggeffects)
library(papaja)
theme_set(theme_few())
knitr::opts_chunk$set(echo=F, warning=F, cache=T, 
                      message=F, sanitize = T)
```

@@

```{r}
roc_data <- gold_sample %>%
  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
  right_join(all_gold_sample_frames_op) %>%
   mutate(hand_detected = hand_detected>0, face_detected = face_detected > 0) %>% # number = number of faces/hands detected
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected)) %>%
  group_by(detection_threshold) %>%
  summarize(tpr_faces = return_tpr(face_eval_ketan), fpr_faces = return_fpr(face_eval_ketan), tpr_hands = return_tpr(hand_eval_ketan), fpr_hands = return_fpr(hand_eval_ketan), )

@@

@@

ggplot(all_detections %>% filter(child_id %in% c('S','A')), 
       aes(x=age_day_bin, y=prop, 
           size=log10(num_frames_total),
           col=region)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + 
  geom_smooth(data = goldset_adult_hands, span=10, aes(weight = num_frames_total), show.legend = FALSE,
              lty = 2, span=10, se = FALSE) +
  geom_smooth(data = goldset, span=10, aes(weight = num_frames_total), show.legend = FALSE,
              lty = 3, span=10, se = FALSE) +
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.6) +
  facet_grid(.~child_id) + 
  theme_few(base_size=10) +
  ggthemes::scale_color_solarized(name = "") + 
  scale_size_continuous(name = "Detections (Log 10)") +
  theme(legend.text=element_text(size=10)) +
  theme(legend.position="bottom")

>>>>

---
title: "Appendix"
author: "Bria Long"
date: "1/6/2022"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r, echo=F, message=F}
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(egg)
library(stargazer)
library(magick)
library(ggeffects)
library(papaja)
library(lme4)
library(xtable)
library(lmerTest)
theme_set(theme_few())
knitr::opts_chunk$set(echo=F, warning=F, cache=T, 
                      message=F, sanitize = T)
```

@@

```{r}
roc_data <- gold_sample %>%
  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
  right_join(all_gold_sample_frames_op) %>%
   mutate(hand_detected = hand_detected>0, face_detected = face_detected > 0) %>% # number = number of faces/hands detected
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected)) %>%
  group_by(detection_threshold) %>%
  summarize(tpr_faces = return_tpr(face_eval_ketan), fpr_faces = return_fpr(face_eval_ketan), tpr_hands = return_tpr(hand_eval_ketan), fpr_hands = return_fpr(hand_eval_ketan), f_faces = return_f_score(face_eval_ketan), f_hands = return_f_score(hand_eval_ketan) )

@@

f_faces = ggplot(data=roc_data, aes(x=detection_threshold, y=f_faces, color=detection_threshold)) +
  geom_point() +
  geom_line() +
  ylim(0,1) +
  xlim(0,1) +
  xlab('Detection Threshold') +
  ylab('F-score') +
  ggtitle('Face detections') +
  theme(legend.position = 'none')

f_hands = ggplot(data=roc_data, aes(x=detection_threshold, y=f_hands, color=detection_threshold)) +
  geom_point() +
  geom_line() +
  ylim(0,1) +
  xlim(0,1) +
  xlab('Detection Threshold') +
  ylab('F-score') +
  ggtitle('Hand detections') +
  theme(legend.position = 'none')

ggpubr::ggarrange(f_hands, f_faces, nrow=1)
ggsave('appendix_figs/f_scores_by_thres.pdf', width = 7, height = 3)
ggsave('appendix_figs/f_scores_by_thres.png', device = "png", width = 7, height = 3)

@@

ggplot(all_detections %>% filter(child_id %in% c('S','A')), 
       aes(x=age_day_bin, y=prop, 
           size=log10(num_frames_total),
           col=region)) +
  geom_point(alpha=.5) +
  # geom_point(alpha=.2, data = goldset) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + 
  geom_smooth(data = goldset_adult_hands, span=10, aes(weight = num_frames_total), show.legend = FALSE,
              lty = 2, span=10, se = FALSE) +
  geom_smooth(data = goldset, span=10, aes(weight = num_frames_total), show.legend = FALSE,
              lty = 3, span=10, se = FALSE) +
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.6) +
  facet_grid(.~child_id) + 
  theme_few(base_size=10) +
  ggthemes::scale_color_solarized(name = "") + 
  scale_size_continuous(name = "Detections (Log 10)") +
  theme(legend.text=element_text(size=10)) +
  theme(legend.position="bottom")
